On the means, costs, and system-level impacts of 24/7 carbon-free energy procurement

### 2023-10-18 manuscript/manuscript.tex
manuscript: move CFE problem from SI to methods
manuscript: internal revision, final minor improvements

We thank the following people for fruitful discussions on the 24/7 carbon-free energy procurement and the art of energy system modelling: Fabian Neumann, Elisabeth Zeyen, Devon Swezey.

@@

We publish an online dashboard with results for the entire scenario space alongside the paper \href{}{DASHBOARD}.

@@

\section{Mathematical formulation of clean energy procurement}
\label{sec:si_3}
\input{sections/supplementary_3.tex}

>>>>

We thank the following people for fruitful discussions on the 24/7 carbon-free energy procurement and the art of energy system modelling: Fabian Neumann, Elisabeth Zeyen, Devon Swezey, Brian Denvir, Marc Oman, Jesse Jenkins and research staff of the Zero carbon Energy systems Research and Optimization Laboratory (ZERO Lab) at Princeton University.

@@

@@

### 2023-10-18 manuscript/sections/conclusion.tex
manuscript: internal revision, final minor improvements

Taken together, we show that 24/7-CFE commitment by corporate sector stakeholders is a step above and beyond the 100\% annual renewable matching in paving the path toward the carbon net-zero energy systems. 
This voluntary commitment also delivers a range of benefits to the society by 
(i) triggering innovation, availability and earlier utilisation of advanced clean firm generation needed for the transformation of energy systems to a complete carbon net-zero state, 
(ii) reducing system emissions, and (iii) reducing system flexibility needs.

>>>>

In this work, we systematically examined the means, costs, and the system-level impacts of the 24/7 carbon-free energy matching. 
We find that 24/7 matching is a viable and effective strategy for electricity buyers aiming to eliminate their own carbon footprint and contribute to wider system decarbonisation.
Voluntary commitments to the hourly matching strategy have a further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.
The evidence holds across geographical locations and is robust to sensitivity analyses.
Even as grids become cleaner over time, the 24/7 matching strategy retains its significance in reducing system-level emissions, which is essential in light of evolving national energy and climate policies.

### 2023-10-18 manuscript/sections/discussion.tex
manuscript: internal revision, final minor improvements

% Where we add: Decarbonisation story
A deeper look at the role of voluntary clean energy procurement commitments in grid decarbonisation reveals that the hourly matching strategy retains its significance in reducing system-level emissions, even as grids become cleaner over time.
We examined two distinct mechanisms through which 24/7 CFE procurement facilitates system decarbonization: \enquote{profile} and \enquote{volume}.
As companies adapt their procurement strategies, it is important to understand how these mechanisms perform across different grid locations and years.
Interestingly, the disparity between the annual renewable (\enquote{volumentric}) matching and 24/7 CFE hourly matching strategies in decarbonisation outcomes becomes ever more evident as electricity grids become cleaner.
This phenomenon illustrates the effectiveness of 24/7 CFE procurement in supporting system decarbonisation within the context of evolving national energy and climate policies.

@@

% on the impact on back up flexibility needs
From a system-wide benefits perspective, voluntary commitments to 24/7 CFE reduce the need for flexibility in background electricity systems. 
There will be less investment in gas-fired peaker generators, as well as less need for battery storage elsewhere in the system.
This effect has been explored by Xu et al. (2022) and Riepin~\&~Brown (2022) \cite{riepin-zenodo-systemlevel247,xu-247CFE-report}

@@

% Excess constraint problem
One of the simplifications of mathematical models implementing 24/7 CFE procurement is how the excess carbon-free electricity is handled. 
The \enquote{excess CFE} can be defined as the total amount of carbon-free electricity supply exceeding the demand of the participating consumers in a given period of time.
Here we assume that the excess can either be curtailed or sold to the regional electricity market at wholesale market prices, until the excess constraint is reached (see \cref{sec:si_3} for detail).
The problem with the uncostrained export of excess CFE to the regional market could be a situation where excess electricity from the renewable generators procured by 24/7 consumers displaces electricity from other renewable generators in the market, which in turn may challenge additionality of the 24/7 procurement; and if system-wide renewable expansion is constrained, the cost-optimal solution may be to use the excess CFE to \enquote{relax} the constraint, increasing the renewable portfolio of participating consumers.
Similar \enquote{spillover effect} problem has been observed and discussed by Xu et al. (2022) \cite{xu-247CFE-SSRN}.
In their white paper, Peninsula Clean Energy team also discuss the problems and implications of the excess supply. Citing their work: \enquote{We conclude that excess supply is a necessary aspect of a time-coincident renewable portfolio in the range of likely market conditions in California today} \cite{peninsula-report247}.
Both studies perform sensitivity analyses on the excess supply and discuss the implications on their findings \cite{xu-247CFE-SSRN, peninsula-report247}.

@@

One of the alternative strategies could be that companies, in their pursuit to reduce system-level carbon emissions, focus on system-wide impact as measured via short-run marginal emissions accounting (\enquote{emissions matching}).
Xu~et~al. (2023) bring this discussion from the realm of arguments into quantitative analysis, concluding that \enquote{emissions matching strategies have zero or near-zero long-run impact on system-level \co emissions} \cite{princeton-247CFEvsEmissionality}.

>>>>

% Where we add: Decarbonisation story
A deeper look at the role of voluntary clean energy procurement commitments in grid decarbonisation reveals that the hourly matching strategy retains its significance in reducing system-level emissions, even as grids become cleaner over time.
We examined two distinct mechanisms through which 24/7 CFE procurement facilitates system decarbonization: \enquote{profile} and \enquote{volume}.
As companies adapt their procurement strategies, it is important to understand how these mechanisms perform across different grid locations and years.
Interestingly, the disparity between the annual (\enquote{volumetric}) matching with renewable energy and 24/7 CFE hourly matching strategies in decarbonisation outcomes becomes ever more evident as electricity grids become cleaner.
This phenomenon illustrates the effectiveness of 24/7 CFE procurement in supporting system decarbonisation within the context of evolving national energy and climate policies.

@@

% on the impact on back up flexibility needs
From a system-wide perspective, voluntary commitments to 24/7 CFE reduce the need for flexibility in background electricity systems. 
There will be less investment in gas-fired peaker generators, as well as less need for battery storage elsewhere in the system.
This effect has been explored by Xu et al. (2022) and Riepin~\&~Brown (2022) \cite{riepin-zenodo-systemlevel247,xu-247CFE-report}

@@

% Excess constraint problem
One of the simplifications of mathematical models implementing 24/7 CFE procurement is how the excess carbon-free electricity is handled. 
The \enquote{excess CFE} can be defined as the total amount of carbon-free electricity supply exceeding the demand of the participating consumers in a given period of time.
Here we assume that the excess can either be curtailed or sold to the regional electricity market at wholesale market prices, until the excess constraint is reached. 
The constraint restricts the volume of excess electricity sold to the regional grid, ensuring it does not surpass 20\% of the annual demand from participating consumers.
The problem with the uncostrained export of excess CFE to the regional market could be a situation where excess electricity from the renewable generators procured by 24/7 consumers displaces electricity from other renewable generators in the market, which in turn may challenge additionality of the 24/7 procurement; and if system-wide renewable expansion is constrained, the cost-optimal solution may be to use the excess clean electricity to \enquote{relax} the constraint, increasing the renewable portfolio of participating consumers.
Similar \enquote{spillover effect} problem has been observed and discussed by Xu et al. (2022) \cite{xu-247CFE-SSRN}.
In their white paper, Peninsula Clean Energy team also discuss the problems and implications of the excess supply. Citing their work: \enquote{We conclude that excess supply is a necessary aspect of a time-coincident renewable portfolio in the range of likely market conditions in California today} \cite{peninsula-report247}.
Both studies perform sensitivity analyses on the excess supply and discuss the implications on their findings \cite{xu-247CFE-SSRN, peninsula-report247}.

@@

One of the alternative strategies could be that companies, in their pursuit to reduce system-level carbon emissions, focus on system-wide impact as measured via short-run marginal emissions accounting (\enquote{emissions matching}).
Xu~et~al. (2023) bring this discussion from the realm of arguments into quantitative analysis, concluding that \enquote{emissions matching strategies have zero or near-zero long-run impact on system-level CO$_2$ emissions} \cite{princeton-247CFEvsEmissionality}. The reason for this, citing the authors, is that voluntary carbon-free energy procurement under this strategy almost exclusively displaces other carbon-free energy rather than fossil fuels.

### 2023-10-18 manuscript/sections/introduction.tex
manuscript: internal revision, final minor improvements

\textbf{Contribution --} The novelty of this study is to go beyond case studies and show in a systematic way, across many regions and levels of energy transition, how voluntary commitments to 24/7 CFE procurement impact participating buyers and regions where voluntary procurement occurs.
We explore different designs, optimal procurement strategies, costs, benefits and system-level impacts of the 24/7~CFE matching approach.
Our analysis focuses on four regions within the European energy system with unique characteristics, and we vary the analysis years to track the evolution of the energy system.
Additionally, we examine the underlying mechanisms that drive the system-level reduction of \co emissions, and examine how they perform over time and across regions. 
This work is a follow-up to the earlier public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results.

@@

The remainder of the paper is structured as follows: \cref{sec:methods} gives a brief summary of methodology, sources of model input data, and the experimental setup. 
The results are presented and discussed in \cref{sec:results} and put in perspective in \cref{sec:discussion}. 
The work is concluded in \cref{sec:conclusion}. 
\nameref{sec:si} provides further details about model assumptions, background energy system parametrisation, and the clean energy procurement mathematical model.

>>>>

\textbf{Contribution --} The novelty of this study is to go beyond case studies and show in a systematic way, across many regions and levels of energy transition, how voluntary commitments to 24/7 CFE procurement impact participating buyers and regions where voluntary procurement occurs.
We explore different designs, optimal procurement strategies, costs, benefits and system-level impacts of the 24/7~CFE matching approach.
Our analysis focuses on four regions within the European energy system with unique characteristics, and we vary the analysis years to track the evolution of the energy system.
Additionally, we examine the underlying mechanisms that drive the system-level reduction of CO$_2$ emissions, and examine how they perform over time and across regions. 
This work is a follow-up to the earlier public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results.

@@

The remainder of the paper is structured as follows: \cref{sec:methods} introduces a mathematical model of clean energy procurement strategies and gives a brief summary of the methodology, sources of model input data, and the experimental setup.
The results are presented and discussed in \cref{sec:results} and put in perspective in \cref{sec:discussion}. 
The work is concluded in \cref{sec:conclusion}. 
\nameref{sec:si} provides further details about model assumptions and parametrisation of the background energy system.

### 2023-10-18 manuscript/sections/methods.tex
manuscript: internal revision, final minor improvements

\textit{100\% annual matching --} The annual volumetric renewable matching strategy is modelled with a constraint (\ref{eqn:RES100}). 
More formally, the sum of all dispatch $g_{r,t}$ of contracted renewable generators $r\in RES$ over the year $t\in T$ is equal to the sum of the annual demand $d_t$ of participating consumers:
\begin{equation}
\sum_{r\in RES, t\in T} g_{r,t} = \sum_{t\in T} d_t
\label{eqn:RES100}
\end{equation}

>>>>

\textit{100\% annual matching --} The annual volumetric renewable matching strategy is modelled with a constraint (\ref{eqn:RES100}). 
More formally, the sum of all dispatch $g_{r,t}$ of contracted renewable generators $r\in RES$ over the year $t\in T$ is equal to the annual electricity demand of participating consumers:
\begin{equation}
\sum_{r\in RES, t\in T} g_{r,t} = \sum_{t\in T} d_t
\label{eqn:RES100}
\end{equation}

### 2023-10-18 manuscript/sections/results.tex
manuscript: internal revision, final minor improvements

Throughout the analysis, we examine how voluntary clean electricity procurement strategies affect both buyers and the electricity system as a whole.
From the \gls{ci} buyers' perspective, we examine optimal procurement strategies (i.e., a mix of locally procured energy generation and storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage, also known as Scope 2 emissions \cite{GHGProtocolScope2}.
From a system perspective, we analyze how voluntary clean energy procurement impacts \co emissions in the region and the \enquote{demand pull} for advanced energy technologies.

@@

Considering the large scenario space, this work presents results for a selection of scenario branches that generalise the system impacts of 24/7 CFE procurements.
We publish an online dashboard with results for the entire scenario space alongside the paper, see \nameref{sec:code}.

@@

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Average emissions rate of participating consumers.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
        \label{fig:10-2025-IE-p1-ci_emisrate}
    \end{subfigure}
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \vspace{-0.2cm}
        \caption{\co emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
        \label{fig:10-2025-IE-p1-zone_emissions}
    \end{subfigure}
    \caption{Impact of clean electricity procurement commitments on emissions of participating consumers (top panel) and the system-level emissions in a local region (bottom panel).}
    \label{fig:10-2025-IE-p1-emissions}
\end{figure}

\cref{fig:10-2025-IE-p1-ci_emisrate} shows how choice of a procurement policy affects the average emissions rate of participating consumers.
Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 177~g\co/kWh in the reference case.
If participating consumers follow 100\%~RES policy, the emission rate is reduced to 60~g\co/kWh.
This yields a considerable emission rate reduction compared to the reference case.
The 24/7~CFE procurement with targets above 85\% helps the participating consumers to reduce emissions further beyond the treshhold set by the 100\%~RES. 
At the 100\% CFE target, participating consumers attain a zero emission rate associated with their electricity consumption, as they perfectly align demand and \gls{cfe} supply on an hourly basis.

Voluntary procurement of clean electricity also helps decarbonise the electricity system as a whole.
We explore this effect by plotting \co emissions in the local region of the participating consumers, i.e. Ireland (\cref{fig:10-2025-IE-p1-zone_emissions}).
Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2 Mt\co/a.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021. A strong decreasing trend is expected, since the Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
The modelling results indicate that a commitment to 100\% 24/7~CFE in 2025 from 10\% of the \gls{ci} electricity demand could yield a reduction in Irish emissions by 0.6~Mt\co/a, in contrast to a scenario absent voluntary procurement. 
This reduction equates to 14\% of the total emissions from the Irish power sector.
100\%~RES can also facilitate system-level \co emissions reductions (as depicted by the left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, 24/7~CFE attains superior emissions reductions when the CFE target surpasses 85\%.

@@

The impact of 24/7 hourly CFE procurement on system-level \co emissions is notable in both Germany and Poland, as depicted in \cref{fig:10-2025-DE-p3-zone_emissions} and \cref{fig:10-2025-PL-p3-zone_emissions}.
In the absence of any procurement strategy, carbon emissions from the power sectors of Germany and Poland are projected to be 118.8~Mt\co and 83.8~Mt\co in 2025, respectively.%
\footnote{Despite Germany consuming more electricity, the similar scale of power sector carbon emissions between the two countries can be attributed to Poland's significantly higher emission intensity in its electricity mix.} 
By engaging in voluntary clean energy procurement, \gls{ci} consumers can drive notable decarbonisation in the local regions, exceeding the benchmarks set by \gls{necp}s.
For instance, in Germany, even a 10\% participation rate under a 100\%~RES policy can diminish national emissions by 11.1~Mt\co annually; remarkably, the 24/7~CFE approach can amplify this impact to up to 14~Mt\co/a, given a CFE target of 100\%.

@@

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{\co emissions in the local region (Germany).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/DE/p3/zone_emissions.pdf}
        \label{fig:10-2025-DE-p3-zone_emissions}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{\co emissions in the local region (Poland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/PL/p3/zone_emissions.pdf}
        \label{fig:10-2025-PL-p3-zone_emissions}
    \end{subfigure}%

@@

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{\co emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/zone_emissions.pdf}
        \label{fig:10-2030-IE-p1-zone_emissions}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \caption{Cost breakdown of a procurement policy: technological palette~1.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/ci_costandrev.pdf}
        \label{fig:10-2030-IE-p1-ci_costandrev}
    \end{subfigure}%

@@

\begin{res}
    24/7 CFE procurement mitigates system-level \co \newline 
    emissions through two distinct mechanisms: \enquote{profile} and \enquote{volume}. The mechanisms origin from distinct aspects of the interplay between the 24/7 CFE procurement and the background electricity grids.
\end{res}

@@

In the previous sections, we demonstrated that 24/7 clean energy procurement results in a substantial reduction of \co emissions in local electricity grids (Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions}).
In this section, we examine the underlying mechanisms that drive these observed reductions, so as to better understand how clean energy procurement and emissions reduction interrelate.

>>>>

Throughout the analysis, we examine how voluntary clean electricity procurement strategies affect both buyers and the electricity system as a whole.
From the \gls{ci} buyers' perspective, we examine optimal procurement strategies (i.e., a mix of locally procured energy generation and storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage, also known as Scope 2 emissions \cite{GHGProtocolScope2}.
From a system perspective, we analyze how voluntary clean energy procurement impacts CO$_2$ emissions in the region and the \enquote{demand pull} for advanced energy technologies.

@@

Considering the large scenario space, this work presents results for a selection of scenario branches that generalise the system impacts of the 24/7 carbon-free energy procurement.
We publish all code to reproduce the experiments under open license alongside the paper. 
See \nameref{sec:code}.

@@

\cref{fig:10-2025-IE-p1-ci_emisrate} shows how choice of a procurement policy affects the average emissions rate of participating consumers.
The average emissions rate is derived by dividing the total CO$_2$ emissions linked to the electricity consumption of participating consumers by the total kilowatt-hours (kWh) consumed.
Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 177~g\co/kWh in the reference case.
If participating consumers follow 100\%~RES policy, the emission rate is reduced to 60~g\co/kWh.
This yields a considerable emission rate reduction compared to the reference case.
The 24/7~CFE procurement with targets above 85\% helps the participating consumers to reduce emissions further beyond the treshhold set by the 100\%~RES. 
At the 100\% CFE target, participating consumers attain a zero emission rate associated with their electricity consumption, as they perfectly align demand and \gls{cfe} supply on an hourly basis.

Voluntary procurement of clean electricity also helps decarbonise the electricity system as a whole.
We explore this effect by plotting CO$_2$ emissions in the local region of the participating consumers, i.e. Ireland (\cref{fig:10-2025-IE-p1-zone_emissions}).
Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2 Mt\co/a.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~MtCO$_2$ in 2021. A strong decreasing trend is expected, since the Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
The modelling results indicate that a commitment to 100\% 24/7~CFE in 2025 from 10\% of the \gls{ci} electricity demand could yield a reduction in Irish emissions by 0.6~Mt\co/a, in contrast to a scenario absent voluntary procurement. 
This reduction equates to 14\% of the total emissions from the Irish power sector.
100\%~RES can also facilitate system-level CO$_2$ emissions reductions (as depicted by the left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, 24/7~CFE attains superior emissions reductions when the CFE target surpasses 85\%.

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Average emissions rate of participating consumers.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
        \label{fig:10-2025-IE-p1-ci_emisrate}
    \end{subfigure}
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \vspace{-0.2cm}
        \caption{CO$_2$ emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
        \label{fig:10-2025-IE-p1-zone_emissions}
    \end{subfigure}
    \caption{Impact of clean electricity procurement commitments on emissions of participating consumers (top panel) and the system-level emissions in a local region (bottom panel).}
    \label{fig:10-2025-IE-p1-emissions}
\end{figure}

@@

The impact of 24/7 hourly CFE procurement on system-level CO$_2$ emissions is notable in both Germany and Poland, as depicted in \cref{fig:10-2025-DE-p3-zone_emissions} and \cref{fig:10-2025-PL-p3-zone_emissions}.
In the absence of any procurement strategy, carbon emissions from the power sectors of Germany and Poland are projected to be 118.8~MtCO$_2$ and 83.8~MtCO$_2$ in 2025, respectively.%
\footnote{Despite Germany consuming more electricity, the similar scale of power sector carbon emissions between the two countries can be attributed to Poland's significantly higher emission intensity in its electricity mix.} 
By engaging in voluntary clean energy procurement, \gls{ci} consumers can drive notable decarbonisation in the local regions, exceeding the benchmarks set by \gls{necp}s.
For instance, in Germany, even a 10\% participation rate under a 100\%~RES policy can diminish national emissions by 11.1~MtCO$_2$ annually; remarkably, the 24/7~CFE approach can amplify this impact to up to 14~Mt\co/a, given a CFE target of 100\%.

@@

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{CO$_2$ emissions in the local region (Germany).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/DE/p3/zone_emissions.pdf}
        \label{fig:10-2025-DE-p3-zone_emissions}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{CO$_2$ emissions in the local region (Poland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/PL/p3/zone_emissions.pdf}
        \label{fig:10-2025-PL-p3-zone_emissions}
    \end{subfigure}%

@@

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{CO$_2$ emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/zone_emissions.pdf}
        \label{fig:10-2030-IE-p1-zone_emissions}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \caption{Cost breakdown of a procurement policy: technological palette~1.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/ci_costandrev.pdf}
        \label{fig:10-2030-IE-p1-ci_costandrev}
    \end{subfigure}%

@@

\begin{res}
    24/7 CFE procurement mitigates system-level CO$_2$ \newline 
    emissions through two distinct mechanisms: \enquote{profile} and \enquote{volume}. The mechanisms origin from distinct aspects of the interplay between the 24/7 CFE procurement and the background electricity grids.
\end{res}

@@

In the previous sections, we demonstrated that 24/7 clean energy procurement results in a substantial reduction of CO$_2$ emissions in local electricity grids (Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions}).
In this section, we examine the underlying mechanisms that drive these observed reductions, so as to better understand how clean energy procurement and emissions reduction interrelate.
